Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-02 paper/structureScene.tex
Edit background section

Computational bioacoustics usually refers to the investigation of sound production, dispersion and reception in animals (including humans) by computational means. A recent paradigm  processes the audio stream in a holistic way over large time-scales, without assuming that a single species is present throughout the recording. Automated systems belonging to this paradigm attempt to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as marking time intervals of particular interest for detailed human inspection \cite{rosenstock2002landbird}.

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
In the closely related field of urban sound environment analysis, a popular approach is the bag-of-frames (BOF) introduced in this context by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Recently, the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, which we believe is a ``skeleton of events on a bed of textures'' \cite{nelken2013} where a few discrete sound events are superimposed upon a stationary acoustic background.
As those distinct and scarce events are most of the time highly relevant for the task at hand, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. For example, studies in the cognitive psychology of urban sound environments have shown that global sound level (perceived or measured) is not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of sound sources which compose the scene. It has been shown that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes. For example, the presence of birds is very likely to be heard in parks in urban areas and so are strong pleasantness indicators. Consequently, research in sound perception is now strongly focused on the contribution of specific sound sources in the assessment of sound environments \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occurring within a given auditory stream may not be discernable, even to human expects, research has shown that a small set of events, so-called markers, suffice to reliably predict many high-level attributes.

From a cognitive psychology perspective, the consensus is therefore that only a few distinct events are sufficient to describe an auditory scene, in contrast to BOF approaches which treat each observation equally when computing summary statistics. A method that takes this knowledge into account could therefore have potential for great impact in the modeling of acoustic scenes.

@@

The methods that performed the best all followed a similar structure, where low-level feature representations, such as MFCCs, were calculated over short windows and fed separately to a classifier, such as an SVM, for training. During the classification stage, the recording to be classified was similarly processed into short windows represented by feature vectors which were classified individually by the classifier and the classifier output was combined over the recording through majority vote. This last step is known as late integration and allows the classifier to work on individual, shorter-scale sound events instead of trying to classify the recording as a whole. By doing this, the classifier is able to identify and exploit the distinct events that characterize the scene instead of trying to model its average structure. This is in agreement with the psychoacoustic results related to the perception of auditory scenes presented above.

>>>>

Computational bioacoustics usually refers to the numerical investigation of sound production, dispersion and reception in animals (including humans). A recent paradigm  processes the audio stream in a holistic way over large time-scales, without assuming that a single species is present throughout the recording. Automated systems belonging to this paradigm attempt to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as marking time intervals of particular interest for detailed human inspection \cite{rosenstock2002landbird}.

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
In the closely related field of urban sound environment analysis, a popular approach is the bag of frames (BOF) introduced in this context by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Recently, the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, which we believe is a ``skeleton of events on a bed of textures'' \cite{nelken2013} where a few discrete sound events are superimposed upon a stationary acoustic background.
As those distinct and sparse events are often highly relevant for the task at hand, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on summary statistics of short-term features.

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. For example, studies in the cognitive psychology of urban sound environments have shown that global sound level (perceived or measured) is not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of sound sources which compose the scene. It has been shown that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes. For example, the presence of birds is very likely to be heard in parks in urban areas and so are strong pleasantness indicators. Consequently, research in sound perception is now strongly focused on the contribution of specific sound sources in the assessment of sound environments \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occurring within a given auditory stream may not be discernable even to human expects, research has shown that a small set of events (so-called markers) suffice to reliably predict many high-level attributes.

From a cognitive psychology perspective, the consensus is therefore that only a few distinct events are sufficient to describe an auditory scene, in contrast to BOF approaches which treat each observation the same and do not incorporate temporal structure between features. A method that takes this knowledge into account could therefore have potential for great impact in the modeling of acoustic scenes.

@@

The methods that performed the best all follow a similar structure, where low-level feature representations, such as MFCCs, are calculated over short windows and fed separately to a classifier, such as a support vector machine (SVM) \cite{cortes-vapnik,cristianini2000introduction}, for training. During the classification stage, a given recording is similarly processed into short windows represented by feature vectors which are classified individually by the classifier. The individial class assignments are then combined through a majority vote which assigns a class to the whole recording. This last step is known as late integration and allows the classifier to work on individual, shorter-scale sound events instead of trying to classify the recording as a whole. By doing this, the classifier is able to identify and exploit the distinct events that characterize the scene instead of trying to model its average structure. This is in agreement with the psychoacoustic results related to the perception of auditory scenes presented above.

\ml{These two last paragraphs are a bit out of place here, since we don't do classification in the paper. Perhaps there is some way to cut them down a bit?}
